---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ramber

<!-- badges: start -->
<!-- badges: end -->

The goal of ramber alllows access to AMBER database, which is a comprehensive European wide database for barriers including dams, weirs, culverts, and fords along river networks. The database has a citizen science option the barrier tracker, which allows users to capture and records barriers. These are submitted to AMBER through a mobile app and then the correctness evalutated by AMBER experts.

## Installation

You can install the development version of ramber like so:

``` r
# install.packages("devtools")

if (!requireNamespace("remotes", quietly = TRUE)) install.packages("remotes")

remotes::install_github("AnthonyBasooma/ramber")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ramber)
## basic example code

getdams <- get_barrieratlas(type = 'dam', country = "AUSTRIA")

head(getdams)
```

